---
title: "Using the `powers` package"
author: "Vincenzo Coia and Thomas Smith"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the `powers` package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

__Note__: This package isn't actually meant to be "serious". I made it just for teaching purposes.

Want to compute powers without having to use `^` or `**`? Give `sqrt` some friends by loading the `powers` package! 

```{r}
library(powers)
```

Want squares, cubes, or reciprocals? Easy.

```{r}
square(1:10)
cube(1:10)
reciprocal(1:10)
```

`apply`-family friendly, too!

```{r}
my_list <- list(1:10, 0.5, -0.7)
## So base-R-boring!
lapply(my_list, function(x) x^2)
## Use powers instead!
lapply(my_list, square)
```

It even comes with the ability to display its output in plot form!

```{r}
reciprocal(1:10, plot_it=TRUE)
```

Let's try using the fractional power functions!

First let's take the square root of a value, or a fractional power of 2
```{r}
squarer(4)
```
 OH wow, amazing!
 
 Next let's try taking the cubic root:
 
```{r}
cubicr(64)
```
 
 Nice and easy!
 
 Now let's do a Box-Cox transformation of a some values
 
```{r}
boxcox(c(2,5,65,78,87))
```
 
Worked like a charm!
